Something about lineage metrics

### 2018-03-28 paper.tex
Update on Overleaf.

% @AML: Currently taking a crack at this bit of the intro (introducing lineages, etc) on paper at the moment! 
A lineage describes a continuous line of descent, linking ancestors and their descendants. A complete lineage can provide a post-hoc, step-by-step guide to the evolution of an extant organism where each step involves replication and inherited variation. Indeed, lineage analyses are a powerful tool for disentangling the evolution of complexity in both natural and digital systems; digital systems, however, allow for

>>>>

% @AML: Currently taking a crack at this bit of the intro (introducing lineages, etc) on paper at the moment! 
A lineage describes a continuous line of descent, linking ancestors and their descendants. A complete lineage can provide a post-hoc, step-by-step guide to the evolution of an extant organism where each step involves replication and inherited variation. Indeed, lineage analyses are a powerful tool for disentangling the evolution of complexity in both natural and digital systems; digital systems, however, allow for fine-grained
